

---
title: "Course Final Project"
author: "Jason Mestrits"
date: "12/20/2020"
output:
  ioslides_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  slidy_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: Developing Data Products - Johns Hopkins Coursera
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(shiny)
library(shinydashboard)
library(tidyverse)

  #  dice_num <- as.numeric(input$dice)
    dice_num <- 3  #manually inputting a value, but in the app this would be dynamic

       ifelse(dice_num == 2, odds_pair <- 6, 
           ifelse(dice_num == 3, odds_pair <- 96,
                  ifelse(dice_num == 4, odds_pair <- 936, odds_pair <- 7056
                  )
           )
    )
    
    ifelse(dice_num == 2, odds_nopair <- 30, 
           ifelse(dice_num == 3, odds_nopair <- 120,
                  ifelse(dice_num == 4, odds_nopair <- 360, odds_pair <- 720
                  )
           )
    )
    
    data1 = data.frame(Outcome = c("Pair", "No_Pair"), Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    

    
    
```

## Intro - My Shiny App

This R Markdown presentation is part of the deliverable for my course project, which is the final assignment in the Johns Hopkins - Developing Data Products Coursera course.

My ui.R and server.R files for my shiny app are available on github and can be located in the "course_project" folder at <https://github.com/mestrits/Rshiny_finalproject>

The following slides will give a brief overview of the functionality in the app.


## Dice Odds Calculator

This shiny app helps you understand the odds of rolling a pair, depending on the number of dice that are are rolled.

- Select the tab in the left hand nav, depending if you want to see the odds or the probability.
- Select the number of dice you would want to roll (2,3,4 or 5) from the drop down
- Observe the responsive chart and text that will update with your selection.

It is worth noting that i didn't finish building out the probability tab... as I would like to watch some football today and my assignment is due.  However, you can see that i could easily update the same script to represent a probability (which is the fraction of the total outcomes on a 0-1 or 0-100% scale.  Odds on the other hand, are based on the number of outcomes) 

## R expression evaluation
Here is a sample calculation to show how i created a data table based on the input value from the app (ie. the # of dice rolled).  I use this table to help construct the stacked barplot viz.

```{r cars, echo = TRUE}

    data1 = data.frame(Outcome = c("Pair", "No_Pair"),
            Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    
    head(data1)
```

## Stacked BarPlot

```{r pressure}

    data1 = data.frame(Outcome = c("Pair", "No_Pair"),
            Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    
ggplot(data1, aes(x = Odds, y = Outcomes, fill = Outcome) ) +
            geom_col() +
            geom_text(aes(label = paste0(Outcomes, " possible outcomes")),
                      position = position_stack(vjust = 0.5)) +
            scale_fill_brewer(palette = "Blues") +
            theme_minimal(base_size = 16) +
            ylab("Outcomes")+
            xlab(" " )

```

