

---
title: "Course Final Project"
author: "Jason Mestrits"
date: "12/20/2020"
output:
  ioslides_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  slidy_presentation: default
  beamer_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: Developing Data Products - Johns Hopkins Coursera
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(shiny)
library(shinydashboard)
library(tidyverse)

  #  dice_num <- as.numeric(input$dice)
    dice_num <- 3  #manually inputting a value, but in the app this would be dynamic

       ifelse(dice_num == 2, odds_pair <- 6, 
           ifelse(dice_num == 3, odds_pair <- 96,
                  ifelse(dice_num == 4, odds_pair <- 936, odds_pair <- 7056
                  )
           )
    )
    
    ifelse(dice_num == 2, odds_nopair <- 30, 
           ifelse(dice_num == 3, odds_nopair <- 120,
                  ifelse(dice_num == 4, odds_nopair <- 360, odds_pair <- 720
                  )
           )
    )
    
    data1 = data.frame(Outcome = c("Pair", "No_Pair"), Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    

    
    
```

## Intro - My Shiny App

My ui.R and server.R files for my shiny app are available on github and can be located in the "course_project" folder at <https://github.com/mestrits/Rshiny_finalproject>

The following gives a brief overview of my app.

This presentation is published at <https://rpubs.com/mestrits/DDP_wk4>

The shiny app can be found at <https://maestroman.shinyapps.io/Shiny_course_project/>

FYI - i had a slick stacked barplot that auto updated with the dynamic input... and it works fine locally but is rendering with an error when hosted on shinyapps.io
Given, that you can still see the text updating, i'm going to submit and trouble shoot further later, however it WAS pretty slick (at least locally)... 
you can see a static version rendered in slide 5




## Dice Odds Calculator

This shiny app helps you understand the odds of rolling a pair, depending on the number of dice that are are rolled.

- Select the tab in the left hand nav, depending if you want to see the odds or the probability.
- Select the number of dice you would want to roll (2,3,4 or 5) from the drop down
- Observe the responsive chart and text that will update with your selection.

FYI - i didn't finish building out the 2nd tab... as I've spent extra cycles trying to figure out my app works locally but i am getting an error when hosting the app at Shinyapps.io.  However, you can see the intent, which is that i could update to have a seperate tab for probability calculation (which is the fraction of the total outcomes on a 0-1 or 0-100% scale.  Odds on the other hand, are based on the number of outcomes) 

## R expression evaluation
Here is a sample calculation to show how i created a data table based on the input value from the app (ie. the # of dice rolled).  I use this table to help construct the stacked barplot viz.

```{r cars, echo = TRUE}

    data1 = data.frame(Outcome = c("Pair", "No_Pair"),
            Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    
    head(data1)
```

## Stacked BarPlot

```{r pressure}

    data1 = data.frame(Outcome = c("Pair", "No_Pair"),
            Outcomes = c(odds_pair,odds_nopair))
    data1 <- data1 %>% mutate(Odds = " ")
    
ggplot(data1, aes(x = Odds, y = Outcomes, fill = Outcome) ) +
            geom_col() +
            geom_text(aes(label = paste0(Outcomes, " possible outcomes")),
                      position = position_stack(vjust = 0.5)) +
            scale_fill_brewer(palette = "Blues") +
            theme_minimal(base_size = 16) +
            ylab("Outcomes")+
            xlab(" " )

```

